JD notes on effects

### 2022-07-21 manuscript/body.tex
modified:   body.tex

>>>>

\jd{After conversation: please re-write this whole section to: describe the “bias” -- talk about Jensen, the problem is that the curve is not actually wrong, but is above or below the points, which is confusing; re-do the plots without any “truth”, the point is to show that bias correction is a sensible way to do it that has the curve closer to the points.}
